PDBF Documentation

### 2015-05-28 Documentation.tex
Fixed mac/linux compatibility. Updated documentation and readme. Added better error message for latex compile errors.

\noindent PDBF toolkit is written in Java and LaTeX and can be used to compile documents on Windows (we are currently working to extend this to Mac and Linux). PDBF documents are also platform independent and run on any desktop OS (Windows, Linux, Mac) with a browser/PDF viewer.\\

@@

\section{SQL queries for PDBF elements}
PDBF uses AlaSQL as database engine. For all available features visit \url{https://github.com/agershun/alasql}. Some functionality might not yet be available because we currently use not the latest version.\\
Mostly sql syntax is standart sql, but for example attributes with spaces in their name have to be sourrounded by square brackets. E.g. SELECT a AS [This is a test] FROM test;\\

>>>>

\noindent PDBF toolkit is written in Java and LaTeX and can be used to compile documents on Windows, Mac and Linux. PDBF documents are also platform independent and run on any desktop OS (Windows, Linux, Mac) with a browser/PDF viewer.\\

@@

\section{SQL queries for PDBF elements}
PDBF uses AlaSQL as database engine. For all available features visit \url{https://github.com/agershun/alasql}. Some functionality might not yet be available because we currently use not the latest version.\\
Mostly sql syntax is standart sql, but for example attributes with spaces in their name have to be sourrounded by square brackets. E.g. SELECT attribute AS [attribute with spaces] FROM test;\\
